---
title: "Team 15 MGT Madness"
output: github_document
---

The goal of MGT Madness was to create a machine learning model that reliably predicted the outcome of both March Madness and regular season college basketball games at a level equal or better to ESPN's industry-standard prediction models.

## Github File Structure

```{r setup, echo=FALSE,message=FALSE,warning=FALSE}
library(tidyverse)
library(data.tree)
```

If you plan to use this repository ensure that you have the following folders stored in the same directory as your .Rproj file. These directories are required to ensure each script runs. Make sure to include each of the .csv and/or .rds data files.

```{r, echo = FALSE,message=FALSE,warning=FALSE}
paths = unique(c(list.dirs(path = "Data",full.names = T),list.files(path = "Data",full.names = T,recursive = TRUE)))
paths = paths[!grepl("deprecated|old",unique(c(list.dirs(path = "Data",full.names = T),list.files(path = "Data",full.names = T,recursive = TRUE))))]
library(data.tree)
library(plyr)

x <- lapply(strsplit(paths, "/"), function(z) as.data.frame(t(z)))
x <- rbind.fill(x)
x$pathString <- apply(x, 1, function(x) paste(trimws(na.omit(x)), collapse="/"))
(mytree <- data.tree::as.Node(x))

```

```{r, echo = FALSE}
paths = unique(c(list.dirs(path = "Final Code",full.names = T),list.files(path = "Final Code",full.names = T,recursive = TRUE)))
library(data.tree)
library(plyr)

x <- lapply(strsplit(paths, "/"), function(z) as.data.frame(t(z)))
x <- rbind.fill(x)
x$pathString <- apply(x, 1, function(x) paste(trimws(na.omit(x)), collapse="/"))
(mytree <- data.tree::as.Node(x))

```

## Data Gathering & Cleaning

Within this directory there are 5 R scripts that were finalized to gather and clean each of our data sources. These scripts utilize numerous data sources such as:

1.  ESPN web API
2.   `hoopR::load_mbb_team_box()` function
3.  <https://www.sports-reference.com/> AP poll data
4.  Google Maps API to geocode arena information

Below are a few examples of our data gathering and cleaning process.

### Men's Basketball Boxscore

This code will use the hoopR package and tidyverse to quickly collect the 2022 box score data for all teams.

```{r, warning=FALSE, message=FALSE}
if (!require('hoopR')) install.packages('hoopR')
if (!require('tidyverse')) install.packages('tidyverse')
mbb_box_score_2012_2022_tbl <- hoopR::load_mbb_team_box(seasons = 2022)

mbb_box_score_2012_2022_tbl %>% head()
```

### AP Poll Data

This function was built to scrape the AP poll data from sports-reference. Both the rvest and tidyverse suite of packages were used. Additional data cleaning was performed in our `data_cleanup.R` script.

```{r, message=FALSE,warning=FALSE}
if (!require('rvest')) install.packages('rvest')
if (!require('tidyverse')) install.packages('tidyverse')
if (!require('glue')) install.packages('glue')

get_ap_polls <- function(year){

  url <- glue::glue("https://www.sports-reference.com/cbb/seasons/men/{year}-polls.html#ap-polls")
  
  webpage <- read_html(url)
  
  data <- html_table(html_nodes(webpage,"table")[1])[[1]]
  names(data) <- c("school","conference",1:ncol(data))
  data <- data %>%
    mutate(year = year)
  
  return(data)
  
}

ap_poll_2012_2022_tbl <- lapply(2012:2022, get_ap_polls) %>% bind_rows()

ap_poll_2012_2022_tbl
```
